SPARQL on the Open, Decentralised Web

### 2016-11-14 dissertation/problems.tex
Mention connected subgraphs in the problems instead
Use sparql macro
remove todo
Go through text flow #18
Note that not all problems addressed, #31, and link to table

We seek to formulate concrete problems that should be solved to
realise the vision formulated in Section~\ref{sec:motivation}. It is
important to note that while some of these issues may be problematic
for the whole Semantic Web community, their only intended scope is the
presented vision.

@@

\begin{problem}\label{prob:unknowndist}
The data distribution is often unknown to the query engine.
\end{problem}
Only simple summary statistics may be available. The discussion of
Example~\ref{ex:bgp} illustrates that even if the distribution of data
given for example a predicate is known, 
\begin{problem}\label{prob:unknownconddist}
\emph{conditional} data distributions are usually unknown to the query engine.
\end{problem}
For example, the population of geographical places may be uniformly
distributed in a given data set, but the population given that the
places are of type city may be a power law. This could have very
significant impact on the overall performance, since in the latter
case, the query planner may consider a BGP like:
\begin{example}{Skew distribution}
\begin{verbatim}
?place ex:population ?population ;
       a ex:City .
\end{verbatim}
\end{example}
as a unit.\todo{Move to preliminaries?}

@@

To understand this, consider Example~\ref{ex:cartesian}, and extend
the BGP to a query with 3 triple patterns. In addition to the two
triple patterns in Example~\ref{ex:cartesian}, add a triple pattern that
connect the two, for example
\rdfterm{?person~foaf:publications~?paper~.}. If the result of this
triple pattern is cached, what is left to evaluate are the two triple
patterns in Example~\ref{ex:cartesian}, which is likely a very
expensive operation.

@@

For example, an underlying SQL store could not compile one query for a
BGP, and could not use a \jcode{WHERE} clause to evaluate a SPARQL
\rdfterm{FILTER}. To remedy this, one could have a method for
evaluating BGPs with (such as the  \pcode{get\_pattern} method of
\pmodule{RDF::Trine}) and without filters, but:

>>>>

We seek to formulate concrete problems that should be solved to
realise the vision formulated in Section~\ref{sec:motivation}. It is
important to note that while some of these issues may be problematic
for the whole Semantic Web community, their only intended scope is the
presented vision. Moreover, many of them are not addressed in this
thesis, but discussed for comprehensiveness. An overview of the
problems and their relation to the published works are included in
Table~\ref{tab:problempaper}.

@@

\begin{problem}\label{prob:unknowndist}
The data distribution is often unknown to the query engine.
\end{problem}
Only simple summary statistics may be available. The discussion of
Example~\ref{ex:bgp} illustrates that even if the distribution of data
given for example a predicate is known, 
\begin{problem}\label{prob:unknownconddist}
\emph{conditional} data distributions are usually unknown to the query engine.
\end{problem}
For example, the population of geographical places may be uniformly
distributed in a given data set, but the population given that the
places are of type city may be a power law. This could have very
significant impact on the overall performance, since in the latter
case, the query planner may consider a BGP like:
\begin{example}{Skew distribution}
\begin{verbatim}
?place ex:population ?population ;
       a ex:City .
\end{verbatim}
\end{example}
as a unit.

@@

To understand this, consider Example~\ref{ex:cartesian}, and extend
the BGP to a query with 3 triple patterns. In addition to the two
triple patterns in Example~\ref{ex:cartesian}, add a triple pattern that
connect the two, for example
\sparql{?person~foaf:made~?paper~.}. If the result of this
triple pattern is cached, what is left to evaluate are the two triple
patterns in Example~\ref{ex:cartesian}, which is likely a very
expensive operation. Another approach to this problem is that of
\cite{papailiou2015graph}, as they insist on caching only connected 
subgraphs.

@@

For example, an underlying SQL store could not compile one query for a
BGP, and could not use a \jcode{WHERE} clause to evaluate a SPARQL
\sparql{FILTER}. To remedy this, one could have a method for
evaluating BGPs with (such as the  \pcode{get\_pattern} method of
\pmodule{RDF::Trine}) and without filters, but:
